Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-10-16 paper.tex
Typo

As intimidating as cryptographers are, the essence of modern symmetric
cryptographic primitives can in fact be distilled in a few paragraph. A
primitive can be understood as a purely functional programs. It takes
two inputs, the input ``cleartext'' and a list of ``round subkeys''
(which are derived from a single key through a non-performance
critical process called ``key schedule'' that we shall ignore here).
The output is the ``ciphertext''. The cleartext, the ciphertext and
each individual round subkeys are processed as ``blocks'' of binary
data. The block size is of order of a hundred bits (typically, 64, 128
or 256 bits).

>>>>

As intimidating as cryptographers are, the essence of modern symmetric
cryptographic primitives can in fact be distilled in a few paragraph. A
primitive can be understood as a purely functional programs. It takes
two inputs: the ``cleartext'' and a list of ``round subkeys''
(which are derived from a single key through a non-performance
critical process called ``key schedule'' that we shall ignore here).
The output is the ``ciphertext''. The cleartext, the ciphertext and
each individual round subkeys are processed as ``blocks'' of binary
data. The block size is of the order of a hundred bits (typically, 64, 128
or 256 bits).
